Heterogeneous Innovation and Intertemporal Productivity Choice

### 2018-02-14 Presentations/Proposal/SE-Proposal.tex
Some changes to law of motion, empirics

\begin{frame}{Framework - Innovation}
	\begin{itemize}\itemsep10pt	
	\item Law of motion: $A_{t+\Delta t} =\begin{cases}
               A_m(1+\alpha^{s})\:,\: \lambda_{inc}\Delta t \:,\: \alpha \in (0,1)\:,\:\ s \in \{1, 2, ...\}\\
               A_t\gamma_{int,abr}\:,\: \lambda_{int,abr}\Delta t\\
               A_t \:, \: \big[1 - \lambda_{inc}\Delta t; 1 - \lambda_{int,abr}\Delta t\big] 
    \end{cases}$
	\item Incremental R\&D cost: $\psi_{inc}(\lambda_{inc}, A_{t}) = \xi_j A_t \lambda_{inc}^{\eta}$
	\item Catching-up: laggards pay $\psi_{inc}(\lambda_{inc}, A_{t})$ and get an arrival $\lambda_{inc} + h$;
	\item Abrupt R\&D cost (for $n_p > 0$): $\psi_{abr}(\lambda_{ext,abr}, \bar{A}_{t}) = \xi_j \bar{A}_t \lambda_{ext,abr}^{\eta}\:$, $\bar{A}_{t}$ sector average;
	%average, to eliminate dependence on R&D level (cst fraction of total expenditure), levels out with returns
	\item Cournot competition: profits $\pi_t$ scale with $\frac{A_{j,i,m}}{\sum_{j}A_{j,i,m}}$ within an industry.
	\end{itemize}
\end{frame}

\begin{frame}{Framework - Innovation}
Outside entrepreneur:
	\begin{itemize}\itemsep12pt	
	%present value eq: of max (dividends, returns) discounted with r
	%rP = D + delP/del t: del = capital gains, D dividends
	\item Value function: $rV_0 - \dot{V}_0 = \max\limits_{\lambda_{ext, abr}}\big[\lambda_{ext, abr}\big[E_j\big[V(A_{t, m+1})\big] - V_0\big] - v \bar{A}_{t}\lambda_{ext, abr}\big]$
 	\item Cost: $C_E(\lambda_{ext, abr}, \bar{A}_{t}) = v \bar{A}_{t} \lambda_{ext, abr}\:$, $v$ a constant;
	\item Free entry condition: $E_j\big[V(A_{t, m+1})\big] = v \bar{A}_{t}$
	\item $\Rightarrow$ Each firm faces an aggregate endogenous creative destruction (CD) of rate $\tau_{CE}$ and internal competition rate $\tau_I$.
	\end{itemize}
\end{frame}

\begin{frame}{Framework - Innovation}
Incumbents:
	\begin{itemize}
	\item Value function: $rV(A_t) - \dot{V}(A_t) =$\vspace{-3mm} $$ \max_{\substack{\lambda_{inc},\:\lambda_{int, abr}\\\lambda_{ext, abr}}}\left[\begin{aligned}
		&\sum_k^{n_{j, p}}\left[\begin{aligned}
			&\qquad\quad\pi_t n_{j, p} - \{\xi_j\lambda_{inc}^{\eta}A_{t,m};\xi_j\bar{A}_t\lambda_{int, abr}^{\eta}\}\\
			&\ \ + \{\lambda_{inc}\big[V(A_{t,m}^{k-}\cup A_{t+\Delta t,m}^{k}) - V(A_{t,m})\big];\\
			& \lambda_{int, abr}\big[E_j\big[V(A_{t,m}^{k-}\cup A_{t+\Delta t,m+1}^{k}\big] - V(A_{t,m})\big]\}\\
			&\quad\ \ - \tau_I\big[V(A_{t,m}\setminus \bar{A}_{t+\Delta t,m}^{k}) - V(A_{t,m})\big]\\
			&\quad- \tau_{CE}\big[V(A_{t,m}\setminus\bar{A}_{t+\Delta t,m+1}^{k}) - V(A_{t,m})\big]
		\end{aligned}\right]\\
		&\quad+ \lambda_{ext, abr}\big[E_j\big[V(A_{t,m}^{k}\cup A_{t+\Delta t,m+1}^{k'}\big] - V(A_{t,m})\big]\\
		&\qquad\qquad\qquad\quad- \xi_j\bar{A}_t\lambda_{int, abr}^{\eta} - \Phi\bar{A}_t
	\end{aligned}\right]$$
	\end{itemize}
	\vspace{-3mm}
	\begin{columns}
	\begin{column}{0.5\textwidth}
	\begin{itemize}\itemsep3pt	
   	\item 1\textsuperscript{st}: instant returns - costs;
	\item 2\textsuperscript{nd}, 3\textsuperscript{rd}: return from int. R\&D;
	\item 4\textsuperscript{th}: internal competition;
	\end{itemize}
	\end{column}
	\begin{column}{0.5\textwidth}
	\begin{itemize}\itemsep3pt	
	\item 5\textsuperscript{th}: external CE;
	\item 6\textsuperscript{th}: return from abr. R\&D;
	\item 7\textsuperscript{th}: Abr. R\&D and fixed costs;
	\end{itemize}    
	\end{column}
	\end{columns}			
\end{frame}

@@

\begin{frame}{Empirical Work - Patents}
Estimation strategy:
	\begin{itemize}\itemsep12pt	
		\item Patent and citation distribution: invariant (at SS);
		\item Need to discipline patent arrival and quality ladder;
		\item Find the "decay rate" of patent quality;
		\item Distinguish external vs. internal (type of citation), abrupt vs. incremental (\# of citations);
		\item Generational productivity step: impose the same shape and compare absolute levels ("envelope").
		%ideally: product cycle data
	\end{itemize}
\end{frame}

@@

>>>>

\begin{frame}{Framework - Innovation}
	\begin{itemize}\itemsep10pt	
	\item Law of motion ($A_{m+1} = A_m\gamma_{int, pot}$): $A_{t+\Delta t} =\begin{cases}
               A_m(1-\alpha^{s})\:,\: \lambda_{inc}\Delta t \:,\: \alpha \in (0,1)\:,\:\ s \in \{1, 2, ...\}\\
               A_t\gamma_{int,abr}\:,\: \lambda_{int,abr}\Delta t\\
               A_t \:, \: \big[1 - \lambda_{inc}\Delta t; 1 - \lambda_{int,abr}\Delta t\big] 
    \end{cases}$
	\item Incremental R\&D cost: $\psi_{inc}(\lambda_{inc}, A_{t}) = \xi_j A_t \lambda_{inc}^{\eta}$
	\item Catching-up: laggards pay $\psi_{inc}(\lambda_{inc}, A_{t})$ and get an arrival $\lambda_{inc} + h$;
	\item Abrupt R\&D cost (for $n_p > 0$): $\psi_{abr}(\lambda_{ext,abr}, \bar{A}_{t}) = \xi_j \bar{A}_t \lambda_{ext,abr}^{\eta}\:$, $\bar{A}_{t}$ sector average;
	%average, to eliminate dependence on R&D level (cst fraction of total expenditure), levels out with returns
	\item Cournot competition: profits $\pi_t$ scale with $\frac{A_{j,i,m}}{\sum_{j}A_{j,i,m}}$ within an industry.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Empirical Work - Patents}
Estimation strategy:
	\begin{itemize}\itemsep12pt	
		\item Patent and citation distribution: invariant (at SS);
		\item Need to discipline patent arrival and quality ladder;
		\item Find the "decay rate" of patent quality;
		\item Distinguish external vs. internal (patent classification or type of citation, could do robustness), abrupt vs. incremental (\# of citations);
		\item Generational productivity step: impose the same shape and compare absolute levels ("envelope").
		%ideally: product cycle data
	\end{itemize}
\end{frame}

@@

\begin{frame}{Appendix: Framework - Innovation}
Outside entrepreneur:
	\begin{itemize}\itemsep12pt	
	%present value eq: of max (dividends, returns) discounted with r
	%rP = D + delP/del t: del = capital gains, D dividends
	\item Value function: $rV_0 - \dot{V}_0 = \max\limits_{\lambda_{ext, abr}}\big[\lambda_{ext, abr}\big[E_j\big[V(A_{t, m+1})\big] - V_0\big] - v \bar{A}_{t}\lambda_{ext, abr}\big]$
 	\item Cost: $C_E(\lambda_{ext, abr}, \bar{A}_{t}) = v \bar{A}_{t} \lambda_{ext, abr}\:$, $v$ a constant;
	\item Free entry condition: $E_j\big[V(A_{t, m+1})\big] = v \bar{A}_{t}$
	\item $\Rightarrow$ Each firm faces an aggregate endogenous creative destruction (CD) of rate $\tau_{CE}$ and internal competition rate $\tau_I$.
	\end{itemize}
\end{frame}

\begin{frame}{Appendix: Framework - Innovation}
Incumbents:
	\begin{itemize}
	\item Value function: $rV(A_t) - \dot{V}(A_t) =$\vspace{-3mm} $$ \max_{\substack{\lambda_{inc},\:\lambda_{int, abr}\\\lambda_{ext, abr}}}\left[\begin{aligned}
		&\sum_k^{n_{j, p}}\left[\begin{aligned}
			&\qquad\quad\pi_t n_{j, p} - \{\xi_j\lambda_{inc}^{\eta}A_{t,m};\xi_j\bar{A}_t\lambda_{int, abr}^{\eta}\}\\
			&\ \ + \{\lambda_{inc}\big[V(A_{t,m}^{k-}\cup A_{t+\Delta t,m}^{k}) - V(A_{t,m})\big];\\
			& \lambda_{int, abr}\big[E_j\big[V(A_{t,m}^{k-}\cup A_{t+\Delta t,m+1}^{k}\big] - V(A_{t,m})\big]\}\\
			&\quad\ \ - \tau_I\big[V(A_{t,m}\setminus \bar{A}_{t+\Delta t,m}^{k}) - V(A_{t,m})\big]\\
			&\quad- \tau_{CE}\big[V(A_{t,m}\setminus\bar{A}_{t+\Delta t,m+1}^{k}) - V(A_{t,m})\big]
		\end{aligned}\right]\\
		&\quad+ \lambda_{ext, abr}\big[E_j\big[V(A_{t,m}^{k}\cup A_{t+\Delta t,m+1}^{k'}\big] - V(A_{t,m})\big]\\
		&\qquad\qquad\qquad\quad- \xi_j\bar{A}_t\lambda_{int, abr}^{\eta} - \Phi\bar{A}_t
	\end{aligned}\right]$$
	\end{itemize}
	\vspace{-3mm}
	\begin{columns}
	\begin{column}{0.5\textwidth}
	\begin{itemize}\itemsep3pt	
   	\item 1\textsuperscript{st}: instant returns - costs;
	\item 2\textsuperscript{nd}, 3\textsuperscript{rd}: return from int. R\&D;
	\item 4\textsuperscript{th}: internal competition;
	\end{itemize}
	\end{column}
	\begin{column}{0.5\textwidth}
	\begin{itemize}\itemsep3pt	
	\item 5\textsuperscript{th}: external CE;
	\item 6\textsuperscript{th}: return from abr. R\&D;
	\item 7\textsuperscript{th}: Abr. R\&D and fixed costs;
	\end{itemize}    
	\end{column}
	\end{columns}			
\end{frame}
